---
title: "DATA_606_Assignment_6"
author: "Md Jalal Uddin"
date: "October 1, 2016"
output: pdf_document
---
                            Problem Set 1 
(1) When you roll a fair die 3 times, how many possible outcomes are there?

```{r}
#Soulution: When we roll a fair die 1 time possible outcomes are Six (1,2,3,4,5,6). When we roll the die 3 times the possible outcomes should be (6X6X6)=216

(Possible_Outcome<- 6^3)  

```


(2) What is the probability of getting a sum total of 3 when you roll a die two times?

```{r}
#Solution: If we roll a die two times there are 6X6=36 possible outcomes. In two ways we can get the sum of the two dies equal to 3 which is (1,2) and (2,1). So, the probability of getting a sum of 3 when rolling a die two times = (2/36)= 0.055555556.

```

(3) Assume a room of 25 strangers. What is the probability that two of them have the same birthday? Assume that all birthdays are equally likely and equal to 1/365. What happens to this probability when there are 50 people in the room?

```{r}
#Solution: I will assume everyone has a unique birthday, and to get the probability of two person have same bithday we will find first that no one has same birthday then  subtract this from 1 to get the probability that at least 2 people share a birthday. 25 people have no same birthday = 365/365) * (364/365)*....*(341/365). And 2 person have same birthday=1-25 people have no same birthday.For 50 people I use similar procedure.

Prob_No_same_bithday_25 <- prod(365:341)/(365^25)
(Prob_two_same_birthday <- 1 - Prob_No_same_bithday_25)

Prob_No_same_bithday_50 <- prod(365:316)/(365^50)

(Prob_two_same_birthday_50<- 1-Prob_No_same_bithday_50)

```


                            #Problem Set 2
                            
                            
```{r}
library(stringr)
library(knitr)
library(dplyr)

```



```{r}

setwd("C:/Users/sql_ent_svc/Desktop/MSDA Assignment/DATA_605/assign6") #assign file
#creating a function
Source_File <- function(d = 1) {
  
  filenamemju <- 'assign6.sample.txt' #selecting file from downladed source.
  
  S_file  <- file(filenamemju, open = 'r', encoding = 'UTF-8-BOM')
  
  lines <- readLines(S_file)
 
  lines <- lines[lines != ''] # removing blank lines from the file
  
  # creating an empty dataframe to store words and counts the words
  words <- data.frame(word = I('a'), count = 0)
  words <- words[FALSE,]
  
  for (line in lines) {
    
    word_text <- str_split(line, '[[:space:]]')
    word_text <- str_replace_all(word_text[[1]], '[^[:alpha:]]', '')
    word_text <-  word_text[ word_text != '']
    # removing empty strings from the line
    
    n <- d - 1
    
    for (i in 1:(length(word_text) - n)) {
      
      text <- tolower(word_text[i:(i + n)]) # convering into lower case
      text <- str_join(text[order(text)], collapse = '.') #deleting the dot
      
      # check if in words; increment if true, add otherwise
      if (text %in% words$word) {
        words[words$word == text, 'count'] <- words[words$word == text, 'count'] + 1
      } else {
        words[nrow(words) + 1,] <- list(text, 1)
      }
      
    }
  }
  
  # finding  probabilities of the counted words
  words$probability <- round(words$count / sum(words$count), 5)
  
  # sorting probabilites in decreasing order. 
  words <- words[order(words$prob, decreasing = TRUE),]
  
  return(words)
}

```

#counting words with probability for single words
```{r}
head(Source_File (1))

```

#counting words with probability for two words
```{r}
head(Source_File(2))

```









                            
                            
                            
                            
                            